Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-02 MS_thesis.tex
Update to reflect changes in ind files
Increase spacing between header and text block

%Add fancy headers with chapter/section titles
\usepackage{fancyhdr}
\setlength{\headsep}{0.9in} %add spacing between header and body text

@@

%Implement the fancy headers for everything from here on out
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[RE]{\rule[-2ex]{0pt}{4ex}\footnotesize\itshape\nouppercase{\leftmark}}
\fancyhead[LO]{\rule[-2ex]{0pt}{4ex}\footnotesize\itshape\nouppercase{\rightmark}}
\setlength{\headheight}{18pt} % as requested by fancyhdf
\renewcommand{\headrulewidth}{0pt}

\renewcommand{\chaptermark}[1]{\markboth{\chaptername \ \thechapter \ :\ #1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection. \ \ #1}{}}

\chapter{Introduction}
\input{ind_files/01_Introduction}
\chapter{Adaptive diversification: a crash course}\label{chap_AD}
\input{ind_files/02_Foundations}

\part{Theory}
\chapter{Population dynamics from stochastic first principles}\label{chap_BD}
\input{ind_files/03_BD_processes}
\chapter{Stochastic field equations for the evolution of quantitative traits}\label{chap_infD_processes}
\input{ind_files/04_field_eqns}

\part{Discussion \& Outlook}
\chapter{A unified view of population dynamics}\label{chap_unification}
\input{ind_files/05_unification_discussion}
%\chapter{Towards a stochastic evolutionary theory}\label{chap_stochasticity}
%\input{ind_files/07_stochastic_discussion}
% \chapter{}
% \input{ind_files/chapter_08}
% \chapter{} <-- uncomment and add as required
% \input{ind_files/chapter_09}

>>>>

%Add fancy headers with chapter/section titles
\usepackage{fancyhdr}
\setlength{\headsep}{1.8in} %add spacing between header and body text

@@

%Implement the fancy headers for everything from here on out
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\rule[-4ex]{0pt}{4ex}\footnotesize\itshape Eco-evolutionary dynamics of finite populations from first principles}
\fancyhead[CO]{\rule[-4ex]{0pt}{4ex}\footnotesize\itshape\nouppercase{\leftmark}}
\setlength{\headheight}{40pt} % as requested by fancyhdf
\renewcommand{\headrulewidth}{0pt}

\renewcommand{\chaptermark}[1]{\markboth{#1}{}} %gets rid of chapter number from header
\renewcommand{\sectionmark}[1]{\markright{#1}} %gets rid of section number from header

\chapter{Introduction}
\input{ind_files/01_Introduction}

\part{Theory}\label{part_theory}
\chapter{Population dynamics from stochastic first principles}\label{chap_BD}
\input{ind_files/02_BD_processes}
\chapter{Stochastic field equations for the evolution of quantitative traits}\label{chap_infD_processes}
\input{ind_files/03_field_eqns}

\part{Summary \& Discussion}\label{part_summary}
\chapter{A unified view of population dynamics}\label{chap_unification}
\input{ind_files/04_unification_discussion}
